Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-07 paper.tex
wake sleep improvements

How should we perform inference for the model
in~\ref{graphicalModel}(a)?
We take inspiration from the Helmholtz machine and the Wake/Sleep algorithm~\cite{hinton1995wake},
which alternates between ``waking'', or training a generative model (our $\mathcal{D},\theta$),
and  ``sleeping'', or training a recognition model on samples from the generative model (our $q$).
For us, a wake cycle means using the recognition model to search for programs that solve the tasks,
while a sleep cycle means updating the DSL and the recognition model
to more closely match the distribution of tasks.
This wake/sleep style of inference is the reason why we call our approach \system.

@@

    \draw [->,thick] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45]{{\footnotesize Trains}} (DSL.30);
    \draw [->,thick] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45]{{\footnotesize Trains}} (recognitionModel.150);
    \draw [->,thick] (DSL.east) to[out = -30,in = 210] node[above]{{\footnotesize Trains}} (recognitionModel.west);

>>>>

How should we perform inference for the model
in~\ref{graphicalModel}(a)?
We take inspiration from the Helmholtz machine and the Wake/Sleep algorithm~\cite{hinton1995wake},
which alternates between ``waking'', which draws samples from a recognition model (our $q$);
and  ``sleeping'', which trains a recognition model on samples from the generative model (our $\mathcal{D},\theta$).
For us, a wake cycle means using the recognition model to search for programs that solve the tasks,
while a sleep cycle means updating the DSL and the recognition model
to more closely match the distribution of tasks.
This wake/sleep style of inference is the reason why we call our approach \system.

@@

    \draw [->,thick] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep)}} (DSL.30);
    \draw [->,thick] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Wake)}} (recognitionModel.150);
    \draw [->,thick] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep)}} (recognitionModel.west);
